Geometric variational problems

### 2020-11-12 NSF2020/Description/preliminarywork.tex
RJR preliminary trimmed significantly

\begin{figure}[!]
\begin{center}
\includegraphics[width=1\textwidth]{figures/PW_fig1A-D.pdf}
\includegraphics[width=1\textwidth]{figures/PW_fig1E-H.pdf}
\end{center}
\vspace{-0.3in}
\caption{\label{fig:tanktreading}\footnotesize (A) A vesicle formed by
  amphiphilic particles in shear flow, and the tank-treading motion
  (B)--(D). The separation of particle pairs in (B) and (C) illustrate
  inter-leaflet slip.  (E)--(G) Tank-treading reaches a steady state in
  elliptical aspect ratio, major-axis angle, and circumference.}
\end{figure}

\section{Preliminary work}
\subsection{Estimating two-dimensional elastic
moduli}
%\section{Preliminary Work on Two-dimensional Vesicle Hydrodynamics in Shear Flow\label{sec:preliminary_work}} 
%\section{Preliminary work on elastic moduli}

To derive a bending modulus, we first considered a planar bilayer subject to a uniform vertical load on the particle centers (Figure \ref{fig:bend}). 
Using a clamped condition at one end, the restoring force in the free part of the bilayer opposes the load.
For small deformations, it is possible to solve the bilayer loading in closed form, and 
this analytical solution (red curve) basically overlaps the midplane of the particle based solution (Figure \ref{fig:bend}A).
We thereby derived a bending modulus $\KB$ in the range 8.51--13.54 \kBT. Throughout the proposal, \kBT\; = 4.11$\times 10^{-21}$ J.
Experimental measurements have accurately determined the bending modulus for several lipid types, with 
typical values lying around 10 \kBT\; \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}.

We also considered the stretching and tilt deformations \cite{Fu2018_SIAM}. 
Stretching occurs whenever there is an excess monolayer area,
and it is energetically costly since it exposes hydrocarbon tails to water.
To measure an area modulus, we stretched a circular vesicle, modeling the cross-section 
of a bilayer tube (Figure \ref{fig:bend}B \& C).
This procedure gave a monolayer area modulus 
34 $\pm$ 2 \kBT \;nm$^{-2}$. Manipulation experiments give a monolayer area modulus in the range 
30--40 \kBT\; nm$^{-2}$ \cite{Nagle17, Nagle17-2}.

Finally, we considered the tilt deformation by applying a fixed tilt angle boundary condition. 
This boundary condition produces a tilt field that decays with the length scale $l = \sqrt{\KB/\KTH}$ 
Fitting to this field, our particle based simulation gave $\lambda = 1.2$ nm, which matches
the value $\KTH \approx 10$ \kBT \; nm$^{-2}$ reported in the literature \cite{KUZMIN2005, KoNa15}.

Nevertheless, the characterization of material properties is incomplete. For one, the preliminary simulations involved relatively low particle numbers (20 to 30), and so we still need to
perform convergence studies with large particle-number systems to arrive at conclusive results. Secondly, we have yet to establish a functional
relationship between the model parameters and elastic moduli.
Finally, to have relevance in physics and biology we must incorporate the remaining twist and saddle splay deformations.
The following simulation outline shows how will achieve aims.

@@

>>>>

\section{Preliminary work}
\subsection{Estimating two-dimensional elastic moduli}
The motivation for Specific Aims 1-3 stemmed from the successful demonstration of gradient driven
self-assembly of amphiphilic particles into two-dimensional micelles,
bilayer membranes, \cite{Fu2018_SIAM}, and recreation of the vesicles tank-treading phenomenon.

Our preliminary work on membrane elasticity 
is particulary encouraging because the effective bending, stretch, and tilt elastic moduli we calculated
were in excellent agreement with the experimental values (Table \ref{tab:moduli}).
The agreement is underscored by the fact we assigned reasonable physical values to 
the main model parameters of HAP energy, rather than tuning parameters.

\begin{table}[h!]
\begin{center}
  \begin{tabular}{|l|p{0.16\textwidth}|l|l|p{0.2\textwidth}|p{0.18\textwidth}}
    \hline
          & simulation type & HAP value        & experimental value & reference\\
    \hline \hline 
    $\KB$ & {\footnotesize uniform load with clamped condition} & $11 \pm 2.5$ \kBT & 10 \kBT                  & \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}\\
    \hline 
    $\KA$ & {\footnotesize bilayer stretching}  & $34$ \kBT $^{-2}$ & 30--40 \kBT $^{-2}$              & \cite{Nagle17, Nagle17-2}\\
    \hline 
    $\KTH$ & {\footnotesize tilt Dirichlet condition} & $12$ \kBT \; nm$^{-2}$ & 10 \kBT $^{-2}$  &  \cite{KUZMIN2005, KoNa15} \\ \hline
  \end{tabular}
\end{center}
\caption{\label{tab:moduli}Comparision of values elastic moduli from the experimental literature and values derived by HAP simulation.}
\end{table}

@@

\begin{figure}
\begin{center}
\includegraphics[width=1\textwidth]{figures/PW_fig1A-D.pdf}
\includegraphics[width=1\textwidth]{figures/PW_fig1E-H.pdf}
\end{center}
\vspace{-0.3in}
\caption{\label{fig:tanktreading}\footnotesize (A) A vesicle formed by
  amphiphilic particles in shear flow, and the tank-treading motion
  (B)--(D). The separation of particle pairs in (B) and (C) illustrate
  inter-leaflet slip.  (E)--(G) Tank-treading reaches a steady state in
  elliptical aspect ratio, major-axis angle, and circumference.}
\end{figure}
